ODGI: understanding pangenome graphs

### 2022-02-17 manuscript/fig_extract_viz_draw_position_untangle.tex
explicit the color

        \textbf{(f)} \REVIEWED{Layout of the C4 pangenome graph made with the \textit{Bandage} tool~\citep{Wick_2015} and} annotated by using \textit{odgi position}. Green nodes indicate the C4 genes. The red rectangle highlights the regions where \textit{C4A} and \textit{C4B} genes differ.

@@

        \textbf{(h)} Visualization of \textit{odgi untangle} output in the C4 pangenome graph: the plots show the copy number status of the sequences in the C4 region with respect to the grch38 reference sequence, making clear, for example, that in HG00438\#2, the \textit{C4A} gene is missing. \vspace{-1em}

>>>>

        \textbf{(f)} \REVIEWED{Layout of the C4 pangenome graph made with the \textit{Bandage} tool~\citep{Wick_2015} and} annotated by using \textit{odgi position}. Green nodes indicate the C4 genes (in red). The red rectangle highlights the regions where \textit{C4A} and \textit{C4B} genes differ.

@@

        \textbf{(h)} Visualization of \textit{odgi untangle} output in the C4 pangenome graph: the plots show the copy number status of the sequences in the C4 region with respect to the grch38 reference sequence, making clear, for example, that in HG00438\#2, the \textit{C4A} gene is missing (white in the middle of the red). \vspace{-1em}
